\documentclass[letterpaper,11pt]{article}
\usepackage{etoolbox}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[normalem]{ulem}
%\usepackage{multicol}
\usepackage[dvipsnames]{xcolor}
\input{glyphtounicode}

%----------FONT OPTIONS---------- sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

% Setting the resume to anon mode
% 0 -> false
% 1 -> true
\newcommand{\setanon}{0}

% VARIABLES
\newcommand{\name}{Mario Moura}
\newcommand{\mail}{mm@mariomoura.com}
\newcommand{\linkedin}{linkedin.com/in/mario-moura/}
\newcommand{\github}{github.com/MarioMoura}
\newcommand{\gpg}{mariomoura.com/mm.gpg}
\newcommand{\website}{mariomoura.com}


\newrobustcmd*\redactifanon[2]{\ifnumequal{\setanon}{0}{#1}{}\ifnumequal{\setanon}{1}{#2}{}}

\newcommand\showname{\redactifanon{\name}{Anon}}
\newcommand\showmail{\redactifanon{\mail}{me@example.com}}
\newcommand\showlinkedin{\redactifanon{\linkedin}{www.linkedin.com}}
\newcommand\showgithub{\redactifanon{\github}{https://github.com/}}
\newcommand\showgpg{\redactifanon{\gpg}{https://example.com}}


\newcommand{\linkedinp}{\showlinkedin}

\newcommand\showwebsite{\redactifanon{\website}{example.com}}

\newcommand{\expandurl}[2]{\href{https://#1}{\uline{#2}}}

\setlength{\tabcolsep}{0in}

% Sections formatting
%\titleformat{\section}{
%\vspace{-4pt}\scshape\raggedright\large
%}{}{0em}{}[\color{black}{\titlerule[0.5pt]} \vspace{-5pt}]
\titleformat{\section}{
	\scshape\center\large\vspace{-5pt}
}{}{0em}{}[\color{black}{\titlerule[0pt]}\vspace{0pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeSkills}[2]{
\item{
    \makebox[4.0cm]{\color{Brown}\textbf{#1} \color{black}\hfill :} #2 \\
    \rule[7pt]{0.98\textwidth}{0.2pt} \\
    \vspace{-0.8cm}
  }
}
\newcommand{\resumeItem}[1]{
\item\small{
    {#1}
  }
}

\newcommand{\education}[4]{
  \vspace{0pt}
\item{
    \color{CadetBlue}\textbf{#1}\color{black} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4} \\
    \rule[7pt]{0.98\textwidth}{0.2pt} \\
    \vspace{-1cm}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}
\item{
    \color{teal}\textbf{#1}\color{black} \hfill #2 \\
    \textit{\small#3} \hfill \textit{\small #4} \\
    \rule[7pt]{0.98\textwidth}{0.2pt} \\
    \vspace{-1cm}
  }
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}
}

\newcommand{\resumeProjectHeading}[3]{
\item
  \color{Sepia}\small\textbf{#1} \color{black}$|$ \emph{#2} \hfill #3 \\
  \rule[7pt]{0.98\textwidth}{0.2pt} \\
  \vspace{-0.7cm}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0.15in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
  \begin{itemize}[rightmargin=0cm ]}
      \newcommand{\resumeItemListEnd}{
    \end{itemize}
}

\newcommand{\resumeCertHeading}[4]{
\item
  \color{RoyalBlue}\small\textbf{#1}
  \color{black} \hfill
  \makebox[2cm]{\emph{#2} \hfill }
  $|$
  \makebox[1.5cm]{#3\hfill}
  --
  \makebox[1.5cm]{\hfill#4} \\
  \rule[7pt]{0.98\textwidth}{0.2pt} \\
  \vspace{-0.7cm}
}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
	\textbf{\Huge \scshape \showname} \\ \vspace{2pt}
	\showmail
	\hspace{1pt} $|$
	\showlinkedin
	\hspace{1pt} $|$
	\showgithub
\end{center}
\begin{center}
	\vspace{-8pt}
	\showgpg
	\hspace{1pt} $|$
	\showwebsite
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{DevOps Engineer}{\redactifanon{Oct 2023 -- Present}{Some Time}}
{\redactifanon{Metaltoad}{Nowhere}}{\redactifanon{ Portland, Oregon (Remote)}{Some city}}
\resumeItemListStart
%\resumeItem{Hardening the security of dozens of CI/CD pipelines by utilizing OAuth-based authentication methods.}
%\resumeItem{Handling multi-stage deployments on Akamai, ensuring proper testing.}
\resumeItem{Developing automatic CDN cache clearing procedures based on content using headless CMSes.}
\resumeItem{Handling Automatic issuance of x509 certificates for Akamai and Cloudfront.}
\resumeItem{Implementing distributed deployments of common CMSs, like Wordpress and Craft.}
\resumeItem{Using Ansible to configure multiple Linux machines, ensuring security and monitoring.}
\resumeItem{Building from the ground up highly available and
scalable Nextjs Infrastructure for $\sim$200,000 users.}
\resumeItem{Making the creation of API endpoints effortless for
the backend team by using Terraform Modules and OpenAPI.}

\resumeItem{Building a Highly available private registry for
  common Terraform modules to distribute them across dozens of
clients.}
\resumeItem{Handling cache purging strategies for CDNs under considerable load ($\sim$200.000 users) using Akamai and Cloudfront.}
\resumeItem{Programming multiple scripts to automatically collect
relevant SOC2 data.}
\resumeItem{Designing and implementing distributed workloads
using Docker and ECS.}
\resumeItem{Reduce operational costs and availability of AWS Elemental Pipelines.}
\resumeItem{Managing Linux boxes for multiple users to
collaborate following specific company standards.}
\resumeItem{Load Testing highly available sites, reaching more
than 200.000+ users.}
\resumeItem{Reduced RDS costs for non-production environments by
49\%.}
\resumeItem{Configured auto-scaling website to handle major
climatic event: Hurricane Milton.}
\resumeItemListEnd

\resumeSubheading
{Systems Administrator}{\redactifanon{Nov 2022 -- Oct 2023}{Some Time}}
{\redactifanon{Metaltoad}{Nowhere}}{\redactifanon{ Portland, Oregon (Remote)}{Some city}}
\resumeItemListStart
\resumeItem{Reduced Terraform CI/CD pipeline runtime in 65.5\%,
  by implementing concurrency. Cutting GitHub Actions cost
by a significant margin.}
\resumeItem{Load tested major applications reaching thousands of
users by leveraging tools like Locust and Jmeter.}
\resumeItem{Made AWS automations, so management tasks would take
minutes instead of hours using mainly Bash and Python.}
\resumeItem{Implemented security measures and policies using AWS
Security Hub, hardening AWS accounts according SOC2.}
\resumeItem{Monitoring with AWS CloudWatch, DataDog and Pingdom,
ensuring $\sim$97\% availability.}
\resumeItem{Backend development using Python on AWS Lambda
coupled with API Gateway.}
\resumeItemListEnd

\resumeSubheading
{Systems Administrator}{\redactifanon{Jan 2020 -- Dec 2024}{Some Time}}
{Independent Consultant}{\redactifanon{Belém, PA, Brazil}{Some city}}
\resumeItemListStart
\resumeItem{Bootstrapped WordPress applications for multiple small
businesses.}
\resumeItem{Deployed and managed email services using Postfix and
Dovecot.}
\resumeItem{Provided consulting work for clients moving to the
cloud.}
\resumeItem{Administrated multiple Linux boxes running LAMP
stacks.}
\resumeItem{Ensured reliability of Debian/Ubuntu and RedHat Linux instances.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
\resumeProjectHeading
{Terraform private registry}{Terraform, MySQL,
Docker, S3, ECS, Bash}{Sep 2024 -- Present}
\resumeItemListStart
\resumeItem{Hosted a highly available version of
  \underline{\href{https://www.terralist.io/}{Terralist}} to leverage SEMVER in
Terraform Module distribution.}
\resumeItem{Developed an automatic CI/CD pipeline for automatic
module publishing using GitOps and GitHub Actions.}
\resumeItem{Enabled live patching of Terraform modules for
subscribed clients.}
\resumeItem{Enabled more secure module distribution by using
isolated credentials.}
\resumeItemListEnd

\resumeProjectHeading {OIDC Terraform Bootstraper}{Bash, Cloudformation, S3, GitHub Actions}{Jun 2023 -- Present}
\resumeItemListStart
\resumeItem{Authenticates to AWS without the need for storing hard credentials.}
\resumeItem{Tool to bootstrap Terraform pipelines securely.}
\resumeItem{Enables Engineers to quickly onboard new clients.}
\resumeItem{Enabled the standardization of all pipelines.}
\resumeItemListEnd

%\resumeProjectHeading {Packit6}{C, Makefile}{Jan 2021 -- Dec 2021}
%\resumeItemListStart
%\resumeItem{Tool to build and inject IPv6 packets into the
%network.}
%\resumeItem{Enables students to experience first-hand uncommon
%scenarios in IPv6 networking.}
%\resumeItem{Allows deep control over protocol headers fields and
%payloads, serving as a hands-on documentation for protocols.}
%\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Certifications}

\resumeSubHeadingListStart
\resumeCertHeading{AWS Security -- Specialist}{Technology}{Mar 2025}{Mar 2027}
\resumeCertHeading{Terraform Associate (003)}{Technology}{Jun
2024}{Jun 2026}
\resumeCertHeading{AWS DevOps Engineer -
Professional}{Technology}{Apr 2024}{Apr 2027}
\resumeCertHeading{AWS SysOps Administrator}{Technology}{Aug 2023}{Apr 2027}
\resumeCertHeading{AWS Cloud Practitioner}{Technology}{Apr
2023}{Apr 2027}
\resumeCertHeading{Duolingo English Test 2021}{Language}{Aug
2021}{Aug 2023}
\resumeCertHeading{IELTS 7.5 2019}{Language}{Oct 2019}{Oct 2021}
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\education
{\redactifanon{CESUPA}{Some college}}{\redactifanon{Belém, PA, Brazil}{Some city}}
{Bachelor in Computer Science}{Jan.
2017 -- Jun 2022}
\resumeSubHeadingListEnd
%\small{
%\setlength\multicolsep{-1pt}
%\setlength{\columnsep}{0.25in}
%\begin{multicols}{3}
%\begin{itemize}[topsep=0pt,leftmargin=0.30in,
%label={$\vcenter{\hbox{\tiny$\bullet$}}$} ]
%\item{AWS DevOps Engineer - Professional}
%\item{AWS Cloud Practitioner}
%\item{AWS SysOps Administrator}
%\item{Terraform Associate (003)}
%\item{Duolingo English Test 2021}
%\item{IELTS 7.5 2019}
%\end{itemize}
%\end{multicols}
%}
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \resumeSkills{Natural
      Languages}{English(Advanced), Portuguese(Native),
      French(Intermediate)}
      \resumeSkills{Languages}{C, Bash, Python, AWK, YAML, HCL}
      \resumeSkills{Frameworks}{React,
        Next.js, WordPress,
      OpenNext, Discourse, \LaTeX, Hugo}
      \resumeSkills{CDNs}{Akamai, Cloudfront}
      \resumeSkills{Developer Tools}{Git,
        Docker, Vim, Linux,
      Bash(as my shell) }
      \resumeSkills{CI/CD}{Github Actions, AWS Code Pipeline}
      \resumeSkills{Cloud Vendors}{AWS(extensive), GCP(limited),
      Vultr, Locaweb, DigitalOcean, Linode}
      \resumeSkills{IaC}{Terraform, CDK, Cloudformation,
      OpenTofu, Ansible, Packer}
      \resumeSkills{Other}{Grafana, Loki, Prometheus, Nginx, Promtail}
    }
\end{itemize}

%-------------------------------------------
\end{document}
